Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-04 latex/manuscript.tex
latex: fix script [ci skip]
This build is based on
https://github.com/greenelab/phenoplier_manuscript/commit/66d20bd8aad49749c3fe842e3d1edbec7bb1b6ac.

This commit was created by the following CI build and job:
https://github.com/greenelab/phenoplier_manuscript/commit/66d20bd8aad49749c3fe842e3d1edbec7bb1b6ac/checks
https://github.com/greenelab/phenoplier_manuscript/actions/runs/5432346759
Merge pull request #81 from greenelab/rev2 [ci skip]
This build is based on
https://github.com/greenelab/phenoplier_manuscript/commit/01398b0990ea0f8bbdbb98e79c0585e2d905a51f.

This commit was created by the

\begin{itemize}
\item
  \textbf{Milton Pividori}\textsuperscript{1,2} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social}
\item
  \textbf{Sumei Lu}\textsuperscript{3}
\item
  \textbf{Binglan Li}\textsuperscript{4} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-0103-6107}{0000-0002-0103-6107}
\item
  \textbf{Chun Su}\textsuperscript{3} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6388-8666}{0000-0001-6388-8666}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/sckinta}{sckinta}
\item
  \textbf{Matthew E. Johnson}\textsuperscript{3}
\item
  \textbf{Wei-Qi Wei}\textsuperscript{5}
\item
  \textbf{Qiping Feng}\textsuperscript{5} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6213-793X}{0000-0002-6213-793X}
\item
  \textbf{Bahram Namjou}\textsuperscript{6}
\item
  \textbf{Krzysztof Kiryluk}\textsuperscript{7} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-5047-6715}{0000-0002-5047-6715}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/kirylukk}{kirylukk}
\item
  \textbf{Iftikhar Kullo}\textsuperscript{8}
\item
  \textbf{Yuan Luo}\textsuperscript{9}
\item
  \textbf{Blair D. Sullivan}\textsuperscript{10} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7720-6208}{0000-0001-7720-6208}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bdsullivan}{bdsullivan}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/blairdsullivan}{blairdsullivan}
\item
  \textbf{Benjamin F. Voight}\textsuperscript{11,12,13} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6205-9994}{0000-0002-6205-9994}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bvoight}{bvoight}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/bvoight28}{bvoight28}
\item
  \textbf{Carsten Skarke}\textsuperscript{13} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-5145-3681}{0000-0001-5145-3681}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/CarstenSkarke}{CarstenSkarke}
\item
  \textbf{Marylyn D. Ritchie}\textsuperscript{1} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-1208-1720}{0000-0002-1208-1720}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/MarylynRitchie}{MarylynRitchie}
\item
  \textbf{Struan F.A. Grant}\textsuperscript{3,14,15,1} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-2025-5302}{0000-0003-2025-5302}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/STRUANGRANT}{STRUANGRANT}
\item
  \textbf{Casey S. Greene}~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8713-9213}{0000-0001-8713-9213}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/cgreene}{cgreene}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/GreeneScientist}{GreeneScientist}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@greenescientist}{@greenescientist@genomic.social}
\end{itemize}

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
{\Letter} --- Correspondence possible via GitHub Issues
or email to
Casey S. Greene \textless casey.s.greene@cuanschutz.edu\textgreater.

@@

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA, USA.
\textsuperscript{5} Vanderbilt University Medical Center.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York, USA.
\textsuperscript{8} Mayo Clinic.
\textsuperscript{9} Northwestern University.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.

@@

>>>>

Milton Pividori\textsuperscript{1,2},
Sumei Lu\textsuperscript{3},
Binglan Li\textsuperscript{4},
Chun Su\textsuperscript{3},
Matthew E. Johnson\textsuperscript{3},
Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9},
Blair D. Sullivan\textsuperscript{10},
Benjamin F. Voight\textsuperscript{11,12,13},
Carsten Skarke\textsuperscript{13},
Marylyn D. Ritchie\textsuperscript{1},
Struan F.A. Grant\textsuperscript{3,14,15,1},
eMERGE Consortium\textsuperscript{*} \&
Casey S. Greene~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
{\Letter} --- Correspondence possible via email to
Casey S. Greene \textless casey.s.greene@cuanschutz.edu\textgreater.

@@

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA 94305, USA.
\textsuperscript{5} Vanderbilt University Medical Center, Nashville, TN 37232, USA.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, NY 10032, USA.
\textsuperscript{8} Mayo Clinic, Rochester, MN 55905, USA.
\textsuperscript{9} Northwestern University, Chicago, IL 60611, USA.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT 84112, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{*}A list of authors and their affiliations appears at the end of the paper.

@@

\hypertarget{emergeconsortium}{%
\subsection{eMERGE Consortium}\label{emergeconsortium}}

Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9} \&
Marylyn D. Ritchie\textsuperscript{1}

%SUPPLEMENTARY_INFORMATION_STARTS_HERE%
